Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-31 manuscript/manuscript.Rmd
added hadcm3 gcm references

Much effort has been spent grappling with the complexity of our natural world in contrast to the relative simplicity of the models we use to understand it.
Heroic amounts of data and computation are being brought to bear on developing better, more realistic models of our environments and ecosystems, in hopes of improving our capacity to address the many planetary crises.
 But despite these efforts and advances, we remain faced with the difficult task of figuring out how best to respond to these crises.
While simplified models have historically allowed for exploration of large decision spaces, the new wave of rich models are applied to highly oversimplified descriptions of potential actions they seek to inform.
For instance, Global Circulation Models (GCMs) such as HadOM3 [CITE] model earth's climate using 1.5M variables, while the comparably vast potential action space is modeled as one of six emissions scenarios from the IPCC [@riahi2017shared].

>>>>

Much effort has been spent grappling with the complexity of our natural world in contrast to the relative simplicity of the models we use to understand it.
Heroic amounts of data and computation are being brought to bear on developing better, more realistic models of our environments and ecosystems, in hopes of improving our capacity to address the many planetary crises.
 But despite these efforts and advances, we remain faced with the difficult task of figuring out how best to respond to these crises.
While simplified models have historically allowed for exploration of large decision spaces, the new wave of rich models are applied to highly oversimplified descriptions of potential actions they seek to inform.
For instance, Global Circulation Models (GCMs) such as HadCM3 [@pope2000impact; @gordon2000simulation; @collins2001internal] model earth's climate using 1.5M variables, while the comparably vast potential action space is modeled as one of six emissions scenarios from the IPCC [@riahi2017shared].
